### 2015-06-18 writing/F'14 paper/cameraready/intro.tex
Cleanup for workshop camera ready.

Tree-structured recursive neural network models (TreeRNNs; \citealt{goller1996learning}) for sentence meaning
have been successful in an array of sophisticated language tasks,
including sentiment analysis \cite{socher2011semi,irsoydeep},
image description \cite{sochergrounded}, and paraphrase detection
\cite{Socher-etal:2011:Paraphrase}. These results are encouraging for
the ability of these models to learn to produce and use strong 
semantic representations for sentences. However, it remains an 
open question whether any such fully learned model can achieve the kind of
high-fidelity distributed representations proposed in recent algebraic
work on vector space modeling 
\cite{ClarkCoeckeSadrzadeh2011,grefenstette2013towards,Hermann-etal:2013,rocktaschellow},
and whether any such model can match the performance of grammars based in logical forms
in their ability to model core semantic phenomena like quantification, entailment, and contradiction \cite{Warren:Pereira:1982,Zelle:Mooney:1996,ZetCol:2005,LiangJordan:2013}.

>>>>

Tree-structured recursive neural network models (TreeRNNs; \citealt{goller1996learning,socher2011semi}) for sentence meaning
have been successful in an array of sophisticated language tasks,
including sentiment analysis \cite{socher2011semi,irsoydeep},
image description \cite{sochergrounded}, and paraphrase detection
\cite{Socher-etal:2011:Paraphrase}. These results are encouraging for
the ability of these models to learn to produce and use strong 
semantic representations for sentences. However, it remains an 
open question whether any such fully learned model can achieve the kind of
high-fidelity distributed representations proposed in recent algebraic
work on vector space modeling 
\cite{ClarkCoeckeSadrzadeh2011,grefenstette2013towards,Hermann-etal:2013,rocktaschellow},
and whether any such model can match the performance of grammars based in logical forms
in their ability to model core semantic phenomena like quantification, entailment, and contradiction \cite{Warren:Pereira:1982,Zelle:Mooney:1996,ZetCol:2005,LiangJordan:2013}.

### 2015-06-18 writing/F'14 paper/cameraready/quantifiers.tex
Cleanup for workshop camera ready.

In each run, we randomly partition the set of valid \textit{single sentences} into train and test, and then label all of the pairs from within each set to generate a training set of 27k pairs and a test set of 7k pairs. Because the model doesn't see the test sentences at training time, it cannot directly use the kind of reasoning described in \S\ref{sec:join} (treating sentences as unanalyzed symbols), and must instead infer the word-level relations and learn a complete reasoning system over them for our logic.

>>>>

In each run, we randomly partition the set of valid \textit{single sentences} into train and test, and then label all of the pairs from within each set to generate a training set of 27k pairs and a test set of 7k pairs. Because the model doesn't see the test sentences at training time, it cannot directly use the kind of reasoning described in \S\ref{sec:join} at the sentence level (by treating sentences as unanalyzed symbols), and must instead jointly learn the word-level relations and a complete reasoning system over them for our logic.
